Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-03-04 paper.tex
Updated figure names

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day.eps}
\caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
\label{DailyAverages}
\end{figure}

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dd12.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset. (b) Same as (a) except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
\label{Storms}
\end{figure}

>>>>

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-50-tak-GOES6.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-day-GOES6.eps}
\caption{$D_{st}$ events from GOES 6. Upper panel: Events in the interval 1989-1991. Lower panel: Events in the interval 1983-1991.}
\label{DailyAverages}
\end{figure}

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-dd12-GOES6.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50$~nT onset. (b) Same as (a) except for constraint that $D_{st}$ stayed below $-50$~nT for at least 12~hours.}
\label{Storms}
\end{figure}
